### 2016-08-05 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated times in the event tables of gas burner report

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
	~(2)~ Middle burner on 				&   180			  &		180			&		180		  \\
	~(3)~ Center burner on 				&   360			  &	   	360			&	   	360		  \\
	~(4)~ West double door opened 		&   420			  &    	420			&	   	420		  \\
	~(5)~ East double door opened 		&   540			  &    	540			&	   	540		  \\
	~(6)~ South exterior door opened 	&   600			  &    	600			&	   	600		  \\
	~(7)~ Center burner off				&   720			  &    	780			&	   	780		  \\
	~(8)~ Middle burner off				&   840			  &    	900			&	   	900		  \\
	~(9)~ Corner burner off				&   960			  &    	1020		&	   	1020	  \\
	(10) PPV fan on 					& 	1260		  &    	1320		&  	   	1320	  \\	
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}
\clearpage

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	~(1)~ All burners on 				& 	0			  &	   1230			&	   2430		\\
	~(2)~ Roof vent opened 				&   128			  &    1320			&	   2520		\\
	~(3)~ West double door opened 		&	153			  &	   1410	 		&	   2610 	\\
	~(4)~ East double door opened 		&   333			  &    1500			&	   2700		\\
	~(5)~ Roof vent closed		 		&   420			  &    1695			&	   2833		\\
	~(6)~ All burners off 				&   550			  &    1815			&	   2970		\\
	~(7)~ Roof vent opened				& 	695 		  &	   1860			&	   3060		\\
	~(8)~ East double door closed		& 	1127 		  &	   2288			&	   N/A		\\
	~(9)~ West double door closed		& 	1140 		  &	   2305			&	   N/A		\\
	(10) Roof vent closed		 		&   1155		  &    2364			&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Seq. 1}	& \textbf{Seq. 2} 	& \textbf{Seq. 3} 	\\
	\midrule
	~(1)~ All burners on 				&	0				&	570				&	1080			\\
	~(2)~ West double door opened 		&	90				&   660				&	1170			\\
	~(3)~ Roof vent opened 		    	&	180				&	720 			& 	1260 			\\
	~(4)~ All burners off 				&	300				&   840				&	1350			\\
	~(5)~ East double door opened		&	345				&   885				&	1420			\\
	~(6)~ Roof vent closed 				&	470				&   1016			&	N/A				\\
	~(7)~ East double door closed		&	497 			&	986				&	N/A 			\\
	~(8)~  West double door closed		&	513 			&	999				&	N/A				\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\clearpage

@@

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of both double doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   195		  		&    133		\\
	~(3)~  1st floor west double door opened 	&	315		  		&    255 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    374		\\
	~(5)~  2nd floor east double door opened	&   586			  	&    501		\\
	~(6)~  PPV fan on 							&   653			  	&    614		\\
	~(7)~  PPV fan off              			&   800			  	&    764		\\
	~(8)~  All burners off 						&   830			  	&    797		\\
	~(9)~  2nd floor south exterior door opened &   899			  	&    850		\\
	(10) PPV fan on 	 						&   1066		  	&    943		\\
	(11) 2nd floor south exterior door closed   &   1179		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

>>>>

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
	~(2)~ Middle burner on 				&   182			  &		181			&		178		  \\
	~(3)~ Center burner on 				&   362			  &	   	361			&	   	359		  \\
	~(4)~ West double door opened 		&   417			  &    	417			&	   	415		  \\
	~(5)~ East double door opened 		&   538			  &    	537			&	   	535		  \\
	~(6)~ South exterior door opened 	&   606			  &    	598			&	   	597		  \\
	~(7)~ Center burner off				&   720			  &    	778			&	   	778		  \\
	~(8)~ Middle burner off				&   841			  &    	898			&	   	897		  \\
	~(9)~ Corner burner off				&   962			  &    	1018		&	   	1019	  \\
	(10) PPV fan on 					& 	1254		  &    	1316		&  	   	1486	  \\	
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}
\clearpage

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	~(1)~ All burners on 				& 	0			  &	   1225			&	   2426		\\
	~(2)~ Roof vent opened 				&   155			  &    1346			&	   2546		\\
	~(3)~ West double door opened 		&	176			  &	   1431	 		&	   2631 	\\
	~(4)~ East double door opened 		&   361			  &    1531			&	   2731		\\
	~(5)~ Roof vent closed		 		&   446			  &    1724			&	   2852		\\
	~(6)~ All burners off 				&   577			  &    1840			&	   2998		\\
	~(7)~ Roof vent opened				& 	722 		  &	   1887			&	   3087		\\
	~(8)~ East double door closed		& 	1149 		  &	   2311			&	   N/A		\\
	~(9)~ West double door closed		& 	1165 		  &	   2331			&	   N/A		\\
	(10) Roof vent closed		 		&   1180		  &    2388			&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Seq. 1}	& \textbf{Seq. 2} 	& \textbf{Seq. 3} 	\\
	\midrule
	~(1)~ All burners on 				&	0				&	566				&	1077			\\
	~(2)~ West double door opened 		&	115				&   685				&	1195			\\
	~(3)~ Roof vent opened 		    	&	208				&	748 			& 	1288 			\\
	~(4)~ All burners off 				&	327				&   868				&	1388			\\
	~(5)~ East double door opened		&	371				&   911				&	1446			\\
	~(6)~ Roof vent closed 				&	495				&   1041			&	N/A				\\
	~(7)~ East double door closed		&	524 			&	1016			&	N/A 			\\
	~(8)~  West double door closed		&	539 			&	1026			&	N/A				\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\clearpage

@@

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of both double doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   195		  		&    133		\\
	~(3)~  1st floor west double door opened 	&	315		  		&    255 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    374		\\
	~(5)~  2nd floor east double door opened	&   586			  	&    501		\\
	~(6)~  PPV fan on 							&   653			  	&    614		\\
	~(7)~  PPV fan off              			&   800			  	&    764		\\
	~(8)~  All burners off 						&   830			  	&    797		\\
	~(9)~  2nd floor south exterior door opened &   899			  	&    850		\\
	(10) PPV fan on 	 						&   1066		  	&    943		\\
	(11) 2nd floor south exterior door closed   &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}
